\documentclass[12pt]{report}
\usepackage[margin=0.75in]{geometry}
\usepackage{listings}

%\usepackage[sfdefault]{GoSans}
\usepackage[T1]{fontenc}


\usepackage{color}
\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
 \definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  backgroundcolor=\color{backcolor},
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}



\title{Singularity on the Farm}
\author{Nick Tyler \\ tylern@jlab.org}


\begin{document}
\maketitle

\section*{Running on the Farm}
Singularity is a container system built to run on server farms and 
supercomputers. A container is similar to a virtual machine but usues the 
underlying kernel of the computer system in order to save on space and overhead 
when using computing recources.  You can test the container interactivly by 
using the ``singularity shell'' command:
\lstinputlisting[language=Bash]{run_local.sh}

This will give you drop you into a shell with all the clas software availible in /usr/local
with the binaries, include files and libraries in their respective folders. They  
are also in the path so everything should run without changes to environment 
variables.

\subsection*{jsub Script}
\quad Following is an example jsub script written in the xml format.  You should 
be able to use your regular Centos 6 submission scripts with only a few modifications. I will 
point out these modifications in the xml format but they should work in the text format as well.
\lstinputlisting[language=Xml]{sing_convert.xml}

There is one major difference to running singularity than running jobs on a Centos 6 machine. 
In the command section instead of running your job script you should run a singularity middle layer script. 
This script runs singularity, which in turn runs your job script. It is discussed more in the following section.


\subsection*{Singularity middle layer script}
\quad The purpose of the middle layer script is to bind the proper disks to the 
singularity container and to then run the image with your desired job script. 
The only things you should modify are the location to the singularity image you want to run, 
and the job script file you want to run.

\lstinputlisting[language=Bash]{run_sing.sh}

\subsection*{Job script}
\lstinputlisting[language=Bash]{job_script.sh}
\pagebreak

\end{document}